---
title: "Week4 Shiny Application and Reproducible Pitch"
author: "Sunil V Nair"
date: "2 December 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This data product used dataset GaltonFamilies, in the HistData R package, to predicts height of child through his gender and the 
height of the parents.

Presentation is being created as part of the peer assessment for the Coursera Developing Data Products. The assignment is geared 
toward ensuring the following concepts were well understood by the students:

  * shiny to build data product application
  * R-Presentation or slidify to create data product related presentations.

##Library used

```{r dl ,echo = TRUE }
library(shiny)
library(HistData)
data(GaltonFamilies)
library(dplyr)
library(ggplot2)

```

##Data preprocessing (converting into centimeters)
     - data(GaltonFamilies)
     - Galton's data on the heights of parents and their children, by child

This data set lists the individual observations for 934 children in 205 families on which Galton (1886) based his cross-tabulation.

##Galton Families Data height in centimeters
```{r cnv , echo = TRUE}

# converting in centimeters
gf <- GaltonFamilies
gf <- gf %>% mutate(father=father*2.54,mother=mother*2.54,childHeight=childHeight*2.54)

```
```{r summ , echo = TRUE}
summary(gf)
```

##Application

To display the understanding of using shiny to build an application, a simple application called Prediction of height of the child through his parents has been developed and deployed at: https://sunilvnair.shinyapps.io/w4ShinyAppReprodPitch/

The application allows the user to:

Select height of parents (mother and father) and gender of child. Make plot and give predicted height of child.

Read the source at: https://github.com/sayids/dataprod

##Thank you.



